Parallel Deduplication with Batch Scheduling for Collocated Virtual Machine Backup in the Cloud

### 2014-01-22 batchdedup/scheduling.tex
Additional cluster histogram added

To determine how evenly distributed VM sizes are, we obtained statistical data
for 22 Aliyun clusters. The clusters in our dataset all have a very long tail distribution,
Though local minima exist in the histogram and the range of VM sizes varies. Other production clusters
may have different distributions, but our findings justify our architecture for a multi-round algorithm.
A representative histogram for one of the clusters is shown in Fig.~\ref{fig:hist-1}. You can see that the range of sizes is very large (the smallest group of 100 VMs has an average size of ~15GB, while the largest has an average size of over 700GB). It is that fact that VM sizes vary greatly that makes the scheduling of VMs to rounds important.

@@

\begin{figure}[ht]
  \centering
  \begin{tikzpicture}
      \begin{axis}[
              ybar interval,
              xlabel=VM Size (GB),
              ylabel=Probability Distribution,
              xtick={50,100,200,300,400,500,600,700,800,900,1000},
      ]
          \addplot+[fill=blue] table[x=MinSize,y=Prob] {figures/AY41A_PD.txt};
      \end{axis}
  \end{tikzpicture}
  \caption{Histogram of average data sizes for a real cluster. TODO:adjust this using the new spreadsheets}
  \label{fig:hist-1}
\end{figure}

>>>>

To determine how evenly distributed VM sizes are, we obtained statistical data
for 22 Aliyun clusters. The clusters in our dataset all have a very long tail
distribution, though local minima exist in the histogram and the range of VM
sizes varies. Other production clusters may have different distributions, but
all of the clusters we have looked at have similarly shaped distributions. Size
distribution histograms for two of the clusters are shown in
Fig.~\ref{fig:hist}. There is a long tail on both histrograms which has been
cut (out to 100GB for the first, and out to 2000GB for the second). The
important thing to get from this data is that in none of the productions
clusters we evaluated was the VM Size distribution flat, which motivates the
importance of round scheduling.

@@

\begin{figure}[ht]
%\centering
\begin{subfigure}%{.5\textwidth}
  \centering
  \begin{tikzpicture}
      \begin{axis}[
              ybar interval,
              width=0.55\linewidth,
                    tick label style={font=\scriptsize},
                    tick style=thin,
              xmax=150,
              xlabel={\tiny VM Size (GB)},
              ylabel={\tiny Percent of VMs},
              xtick={0,50,100,150,200,250,300,400,500,600},
      ]
          \addplot+[fill=blue] table[x=MinSize,y expr=\thisrow{Prob}*100] {figures/AY41A_PD.txt};
      \end{axis}
  \end{tikzpicture}
  %\caption{Histogram of average data sizes for a real cluster.}
  \label{fig:hist-AY41A}
\end{subfigure}
%
%
\begin{subfigure}%{.5\textwidth}
  \centering
  \begin{tikzpicture}
      \begin{axis}[
              ybar interval,
              width=0.55\linewidth,
                    tick label style={font=\scriptsize},
                    tick style=thin,
              xmax=150,
              xlabel={\tiny VM Size (GB)},
              ylabel={\tiny Percent of VMs},
              xtick={0,50,100,150,200,250,300,400,500,600},
      ]
          \addplot+[fill=blue] table[x=MinSize,y expr=\thisrow{Prob}*100] {figures/AY41H_PD.txt};
      \end{axis}
  \end{tikzpicture}
  %\caption{Histogram of average data sizes for a real cluster.}
  \label{fig:hist-AY41H}
\end{subfigure}
\caption{Histograms of average VM sizes for several production clusters}
\label{fig:hist}
\end{figure}
